Designing Types for R, Empirically

### 2020-09-04 paper/main.tex
Added a section about kaggle

\input{corpus.tex}
\input{macros/macros.tex}
\input{asserts.tex}

@@

>>>>

\input{corpus.tex}
\input{macros/macros.tex}
\input{asserts.tex}
\input{kaggle.tex}

@@

\paragraph{User code}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
To represent end-user code in the corpus, we turned to Kaggle, an online
platform for data-science and machine-learning. The website allows people to
share data-science competitions, data-analysis problems together with data, for
which users try to find the best solution. The solutions, called \emph{kernels},
are then shared back to the platform in the form of either plain scripts or as
notebooks. One of the most popular competition is about predicting passenger
survival on Titanic\footnote{\url{https://www.kaggle.com/c/titanic}} with
\KaggleDownloaded kernels in R (over 1/4 of all available R kernels) which we
used for our corpus.

Unlike CRAN, Kaggle is not a curated repository and therefore there are no
guarantees about the quality of the code. After downloading all of the
\KaggleDownloaded kernels and extracting the R code from the various
formats,\footnote{We use {\sf rmarkdown} to convert from notebooks to R.} we
found that \KaggleDuplicated were whole-file duplicates
(\KaggleDuplicatedRatio). From the resulting \KaggleRunnable kernels,
\KaggleFail failed to execute. Next to various runtime exceptions, common
problems were missing libraries (no longer available for R 3.5), parse errors
and misspelled package names. The final set contains \KaggleSuccess kernels with
\KaggleSuccessCodeRnd lines of R code. The Kaggle kernels are used for additonal
validation of the inferred types.
